\newpage
\section{Introduction}

Intelligent surface water treatment can be a valuable asset to reduce the need for ground water extraction. A typical challenge of surface water treatment is determining the quality of the input water. The objective during this graduation project is to explore new ways in which this water can be autonomously monitored in local, remote, and harder to measure locations. Specifically, this project will be taking a look at the use of unmanned aerial vehicles (drones) to do this task. 

It would allow users to measure various water quality variables across an area by using unmanned aerial vehicles and various different water quality sensor concepts. Future projects could mature by for example improving a specific sensor concept or by spotting data trends to automatically determine the best filtration settings.

\input{040_background/00_main}

\subsection{The Research Problem}
The research question that the project made an attempt to answer is as follows:\vspace{3mm}

\large{What is the best way to build a mobile surface water quality sensoring system that can take samples in remote areas?}\vspace{3mm}\\
\normalsize


\subsection{Development Method}
In the plan of action's project activities, there was no description of any specific development method, like scrum or the waterfall model. Instead, a mix of classical and agile development methods were used during the project.\\

While the preference within academics usually go toward tried and tested methods, I found that none of them really fit well with the project's scope and the fact that I am the sole developer.\\

The project consisted of several sprints all conforming to a competence. The sprints were individually managed using kanban \cite{kanban} boards. Due to planning and the reiterative nature of the project, some of these sprints overlapped with each other. How they were planned to overlap is found in the project schedule.\cite{projectplan}\\

\input{050_scope/00_main}
\input{060_approach/00_main}
\subsection{Structure of this report}
Relevant findings from the design, realisation, and conclusion of this project can be found in this report. In the design section, an overview of the working architecture is designed, along with several prototypes. This design is realized and tested in the testing section. The interpretation of these tests can be found in the conclusion section. Further findings that are useful in this project are contained in the preliminary research report, found in the appendix. \cite{prr}