\newpage
\section{Scope}
What falls within the project’s scope and what does not is frequently  unclear. Boundaries are described in order to prevent unclear situations from developing. This project uses \gls{MoSCoW} prioritization to clearly define these boundaries. \cite{moscow}

Given the expertise of the project producer, feasibility of scope, and the yet to be fully discovered field of \gls{UAV} remote sensing, the project focuses on remote water sensing using drones.

\subsection{Must Have}
\begin{itemize}
  \item The project must deliver one working prototype.
  \item The project must deliver every report described in project activities.
  \item The project must receive adequate funding.
  \item There must be accommodations to be able to test out the prototypes in the correct conditions.
\end{itemize}
\subsection{Should Have}
\begin{itemize}
  \item The project should contain well documented software that adhere to industry standards.
  \item The project should have multiple working prototypes.
\end{itemize}
\subsection{Could Have}
\begin{itemize}
  \item The project could deliver a \gls{MVP} for water quality measurement using drones.
  \item The prototypes could have wireless transmission to a server for automated logging.
\end{itemize}
\subsection{Won’t Have this time}
\begin{itemize}
  \item The prototypes won't cover any water quality measurement methods that doesn't involve a drone.
  \item The project will not result in product(s) ready for commercial use.
  \item The research report will not make claims about measurement performance outside of Vietnam
\end{itemize}